---
title: "PML - Course Project"
author: "Diego Taccone"
date: "24/7/2020"
output:
  pdf_document: default
  html_document: default
---

## Summary

The objective of the project is to predict the manner in which a series of 20 subjects performed an exercise.

The outcome is the "classe" variable, which classifies if the exercice was performed in either of five different fasions: Class A, B, C, D or E.

We will analyze the Weight Liftting Excersices dataset, create a predictive model with the training dataset, and test its out of sample error on the test data set.

## Data Download and Preparation

We download and clean the data.  Variables without values and NA´s are eliminated from the dataset, both in the training and the testing sets.

```{r dataclean}
data <- read.csv("training.csv")
testing <- read.csv("testing.csv")
dataclean <- data[,!is.na(data[1,])]
dataclean <- dataclean[,dataclean[1,] != ""]
dataclean$classe <- as.factor(dataclean$classe)
testing <- testing[,!is.na(testing[1,])]
```


## Analysis

Being a classification problem, the approach will be first the check de accuracy of a simple classification tree, then a Random Forest.

For this, we will subset the training set, we called **data** into a training and testing set, being 70% training and 30% testing.  We will train the model with this sub training set, then measure the accuracy on the sub testing set.

The training function in the caret package will be used, and will be set to perform a 25 Bootstrap Cross Validation.

```{r classification tree}
library(caret)
inTrain <- createDataPartition(dataclean$classe,p=0.7,list = FALSE)
training <- dataclean[inTrain,]
testset <- dataclean[-inTrain,]
modFit <- train(classe~.,method = "rpart",data = training[,-c(1,2)])
modFit$resample
```

In this first model, we see that the Accuracy is very low.  

We now try with Random Forests and check te accuracy on the Bootstrap Samples.

```{r random forests}
modFit1 <- train(classe~.,method = "rf",data = training[,-c(1,2)])
modFit1$resample
```

We can observe on the results that we have a very high accuracy on trained model.

We check accuracy with the test set.

```{r test set}
predTest <- predict(modFit1,testset[,-c(1,2)])
confusionMatrix(predTest,testset$classe)
```

Observing the values of the confusionMatrix, we can see the very high accuracy this Random Forest model achieves on our test set.

## Prediction of 20 samples

Now we have selected our model, we can predict our values for the 20 samples.

```{r validation}
predVal <- predict(modFit1,testing[,-c(1,2,60)])
predVal
```

These predicted values where 100% percent certain in the prediction quiz asociated with the project.
                   